Fail Faster

### 2025-03-11 paper/paper.tex
incorporate bcp comments

@@

\begin{lstlisting}

module Gen = struct
  type 'a t = int code -> Random.t code -> 'a code

@@

>>>>

\bcp{The current introduction says, roughly, ``We took a look at
  base.quickcheck, noticed some inefficiencies, applied known
  techniques from staged metaprogramming to eliminate them, and
  observed that speed went up.''  I think we can make much stronger
  claims, but I'm not sure about exactly how strong or what belongs in
  the foreground...
  \begin{itemize}
  \item One of the first serious uses of staged metaprogramming in anger?
  \item A use of staged metaprogramming that is novel / challenging in
  itself, in some way?
  \item An analysis of sources of inefficiency across a range of PBT
  frameworks (and a solution that applies to many of them)?
  \item A usable tool that addresses and overcomes some significant
  implementation challenges?
  \item Careful measurements showing where the sources of inefficiency
  are in existing PBT tools, and which ones matter most?
  \item (Your claim here...)?
  \end{itemize}
}

@@

\begin{lstlisting}
module Gen = struct
  type 'a t = int code -> Random.t code -> 'a code

@@

\bcp{How much faster could we go if we changed the effect ordering?
  If it might be a lot, then should we measure this too?}
